Community Analysis

### 2022-07-30 R/08-community-analysis.Rmd
figure and test updates for poster and draft to brendan

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
p_beta <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage") +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())

>>>>

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
p_beta <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
